Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-25 data_appendix_all_years.Rmd
Fixing a typo and replacing the not working code with female with working code. Problem appears to be related to the "haven labelled" data category.

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012) %>%

@@

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income))
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

>>>>

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)

@@

```{r regression variable specifications}
reg_data <- total_subset %>%
  mutate(ln_income = log(income),
         literate = literacy - 1,
         female = case_when(sex == 2 ~ 1,
                            sex == 1 ~ 0),
         no_assist = assist - 1,
         not_registered = register - 1,
         year_factor = as.factor(year))
